%% Copyright 1998 Pepe Kubon
%%
%% `apptwo.tex' --- 2nd appendix for thes-full.tex from
%%                  the `csthesis' bundle
%%
%% You are allowed to distribute this file together with all files
%% mentioned in READ.ME.
%%
%% You are not allowed to modify its contents.
%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%        Appendix 2
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Illustrating Lists}\label{app:lists}
\index{formatting of Lists}

This appendix is present only in the full version of the thesis. It
illustrates in more detail the formatting of the Lists of Tables,%
\index{List of Tables}\index{List of Figures} Figures, etc. In
addition, it also illustrates the use of the ``other list'' facility
of \textsf{csthesis.sty}\index{csthesis.sty@\textsf{csthesis.sty}}.
Let us start with the latter.

\section{List of Programs}
\index{List of Programs}

In the preamble of \texttt{thes-full.tex}%
\index{thes-full.tex@\texttt{thes-full.tex}}, a new type of a floating
environment---\texttt{program}%
\index{program environment@\texttt{program} environment}---is defined,
together with the \verb+\otherlist+%
\index{otherlist@\texttt{\symbol{'134}otherlist}} command for
typesetting the List of Programs. The list is formatted in the same
way as the lists of Figures and Tables, and an appropriate entry is
added into Contents.

Because programs are defined here as floating environments, they are
typeset with the same (tighter) line-spacing%
\index{spacing in programs} as figures and tables:

\begin{program}[htbp]
  \begin{center}
    This shows that single line spacing\\
    is used inside programs.
    \caption{Example of the new \texttt{program} environment\label{prog1}}
  \end{center}
\end{program}
%
\vspace*{-.3in}
\begin{program}[htbp]
  \begin{center}
    A second example of a program environment.
    \caption{Second program\label{prog2}}
  \end{center}
\end{program}

\section{Formatting of Lists}

The tables (figures, programs, etc.) are organized and sorted by
chapters (appendices), with additional small vertical space separating
the chapter blocks. To illustrate this, I include two new tables here
(see List of Tables, etc., in the beginning of the thesis for the
result)\index{formatting of Lists}:

\begin{table}[htbp]
  \begin{center}
    To be silly or not to be silly\\
    \emph{that} is the question!
    \caption{First meaningless table in Appendix~\ref{app:lists}}
  \end{center}
\end{table}
%
\vspace*{-.3in}
\begin{table}[htbp]
  \begin{center}
    $F = nd^{2}$
    \caption{Second meaningless table in Appendix~\ref{app:lists}}
  \end{center}
\end{table}

